\documentclass[12pt, fleqn, paper=letter]{scrartcl}

%Conserve space
\newcommand{\margin}{0.375in}
\usepackage[margin=\margin,  includehead=false, includefoot=false]{geometry}	%Fixed margins
\usepackage[compact]{titlesec}		%Reasonably compact section spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.3\baselineskip}

%Floats/images setup
\renewcommand{\topfraction}{0.85}	%Fixes float spacing
\renewcommand{\textfraction}{0.1}			
\renewcommand{\floatpagefraction}{0.75}
\usepackage{graphicx}				%Basic image support
	\graphicspath{{/Users/fred/Library/TeXShop/Images/}{./Images/}}
	\usepackage[space]{grffile}
\usepackage[labelfont={bf}, margin=20pt]{caption}		%Caption Placement

% font and date format
\usepackage{newtxtext}
\setkomafont{disposition}{\bfseries}
\usepackage{fancyref}			%Automatically adds Table (tab:' ') or Figure (fig:' ')
\usepackage[UKenglish]{babel}		%UK date format
\usepackage[UKenglish]{datetime}
\let\dateUKenglish\relax
\newdateformat{dateUKenglish}{\THEDAY~\shortmonthname[\THEMONTH]
\twodigit\THEYEAR}

%Math/science
\usepackage{siunitx}	%SI unit : \si{\'unit'} or \SI{#}{\'unit'}
\sisetup{detect-all}
%\usepackage{chemfig}	%Write chemical formulas
\usepackage{mathtools}	%Basic math an extension of amsmath
%\usepackage{amsbsy}	%Bold math
%\usepackage{amstext}	%Text within math environment 

%\usepackage{amssymb}	%Added symbols
%\usepackage{latexsym}	%More added symbols 	
%\usepackage{xfrac}	%Slant fractions / increase fraction display options


%Misc Useful
%\usepackage{lipsum}	%Generates filler text
%\usepackage{tabularx}	%Variable table width spacing
%\usepackage{booktabs}
%\usepackage{multirow}	%Multiple row spanning in tables : \multirow{#}{width}{'text'}
\usepackage{multicol}	%Multiple cols : command \multicols{#}{'text'}

%\usepackage{hyperref}	%Hyperlinking references
\usepackage{enumitem}	%Enumeration control

%\usepackage{fontspec}
%\setmainfont{DINAlternate}

\newcommand{\copiesperpage}{2}
\newcommand{\temp}{
\begin{minipage}[t][
	(\textheight - \margin * (\copiesperpage - 1))/\copiesperpage]{\textwidth}
\textbf{\Large Self-Advocacy Activity
	\hfill Name: \rule{60mm}{1pt}
	Hour: \rule{20mm}{1pt}}

Directions:
Complete each task listed below.
Once you have completed a task, have your teacher sign off on it.

\textbf{Tasks:}
\begin{enumerate}[label={\rule{10mm}{0.4pt} \arabic*)},
	leftmargin=20mm]
\item Complete the “Student Information Sheet” on Schoology.

\item Under Documents on your computer, create a folder for English, Science, Math, and Success.

\item Save the “Student Information Sheet” to your Science folder.

\item Submit the “Student Information Sheet” assignment to Schoology.

\item Send an email to your teacher answering the following question, you must include the why to get credit!
\emph{\quote 
You are principal for a week.
What changes would you want to make in school?
Why would you make these changes? 
}

\item In Schoology, send a message to your teacher answering the following question:
\emph{\quote
What is your definition of success?
What will make you feel successful this school year?  
}

\item Read and respond back to the comment your teacher posted to your “Student Information Sheet” assignment.

\item Check your response from your teacher. in Schoology in your messages

\end{enumerate}

\end{minipage}}

%Document
%===================================
\begin{document}

\temp
\vfill
\temp
































\end{document}